R for Clinical Study Reports and Submission

### 2023-01-13 slides/fda-workshop-slides.Rmd

- Data manipulation: `tidyverse`, `dplyr`, `tidyr`, `ggplot2` etc.
- ADaM data: `adsl`, `adae` etc.

@@

- `tidyverse`: a collection of R packages to simplify the workflow to manipulate,
visualize and analyze data in R.

- `r2rtf`: an R package to create production-ready tables and figures in RTF format.

@@

- `r2rtf` is an R package to create production-ready tables and figures in RTF format.

`r2rtf` is designed to:

- provide simple "verb" functions that correspond to each component of a table,
  to help you translate a data frame to a table in RTF format;
- enable pipes (`%>%`);
- only focus on the **table format**.
  - Data manipulation and analysis should be handled by other R packages. (e.g., `tidyverse`)

@@

`r2rtf` is designed to enable pipes (`%>%`).

@@

`r2rtf` package provides the flexibility to customize table appearance for

@@

`r2rtf` package also provides the flexibility to convert figures in RTF format.

@@

`r2rtf` provides simple "verb" functions that correspond to each component of a table,
  to help you translate data frame to tables in RTF file.

>>>>

- Data manipulation: tidyverse, dplyr, tidyr, ggplot2 etc.
- ADaM data: `adsl`, `adae` etc.

@@

- tidyverse: a collection of R packages to simplify the workflow to manipulate,
visualize and analyze data in R.

- r2rtf: an R package to create production-ready tables and figures in RTF format.

@@

- r2rtf is an R package to create production-ready tables and figures in RTF format.

r2rtf is designed to:

- provide simple "verb" functions that correspond to each component of a table,
  to help you translate a data frame to a table in RTF format;
- enable pipes (`%>%`);
- only focus on the **table format**.
  - Data manipulation and analysis should be handled by other R packages. (e.g., tidyverse)

@@

r2rtf is designed to enable pipes (`%>%`).

@@

r2rtf package provides the flexibility to customize table appearance for

@@

r2rtf package also provides the flexibility to convert figures in RTF format.

@@

r2rtf provides simple "verb" functions that correspond to each component of a table,
  to help you translate data frame to tables in RTF file.

### 2023-01-13 tlf-population.Rmd

To calculate the numbers and percentages of participants by groups, we
provide a simple (but not robust) wrapper function, `count_by()`, using
the `dplyr` and `tidyr` package.

@@

Now we combine individual rows into one table for reporting
purpose. `tbl_pop` is used as input for `r2rtf` to create the final
report.

@@

- Step 1: Read data (i.e., `adsl`) into R.
- Step 2: Bind the counts/percentages of the ITT population, the
  efficacy population, and the safety population by row using the
  `count_by()` function.
- Step 3: Format the output from Step 2 using `r2rtf`.

>>>>

To calculate the numbers and percentages of participants by groups, we
provide a simple (but not robust) wrapper function, `count_by()`, using
the dplyr and tidyr package.

@@

Now we combine individual rows into one table for reporting
purpose. `tbl_pop` is used as input for r2rtf to create the final
report.

@@

- Step 1: Read data (i.e., `adsl`) into R.
- Step 2: Bind the counts/percentages of the ITT population, the
  efficacy population, and the safety population by row using the
  `count_by()` function.
- Step 3: Format the output from Step 2 using r2rtf.
